SoK: The Evolution of Web Application Attack Defenses

### 2014-10-23 docs/questioning.tex
first steps in introduction

% Notes
The attacks we examine include
{\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

>>>>

Web application attacks may involve security misconfigurations,
broken authentication and session management, and other issues.
Some of the most dangerous web application attacks though
are associated with the processing of external input data
that may contain malicious code, a vulnerability known as
code injection.

Such attacks include Cross-Site Scripting ({\sc xss})
attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}
and others. Attacks like these top the vulnerability
lists of numerous bulletin providers like
the Open Web Application Security
Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
({\sc owasp}) and {\sc mitre}\footnote{\url{http://cwe.mitre.org/top25/}}
for several years. Consider the case of {\sc owasp}'s Top
Ten project whose main goal is to raise awareness about
web application security by identifying some of the most
critical risks facing organizations which is referenced by
numerous researchers. In its three consecutive Top Ten lists
(2007, 2010, 2013), different source code-driven injection attacks
dominate the top five positions. This indicates that apart from
the fact that malicious users find new ways to bypass defense
mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
